---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  fig.path = "README-"
)

library(readr)
```

### hashtag

hashtag is a compilation of commands from different twitter and sentiment analysis packages that help you do simple twitter scrapes and analyses - fast.

So far, only "afinn" sentiment analysis is available, which classifies words as 'positive' or 'negative' with an appropriate score. Give it a try!

Note, the user must set up their own twitter API connection. I found this site helpful: [rStatistics.net](http://rstatistics.net/extracting-tweets-with-r/)

### Installation
```{r, echo = TRUE, eval = FALSE}
devtools::install_github("sk6aus6/hashtag")
```

```{r}
library(hashtag)
library(readr)
library(twitteR)
```



### Quick demo

First connect to Twitter. I store my twitter API keys in a file buried deep in my computer:

```{r}
keys <- read_csv('/Users/yam/OneDrive/shared files/Statslearningcourse/twitteR/keys.csv')

# setup_twitter_oauth(consumerKey, consumerSecret, accessToken, accessTokenSecret)

setup_twitter_oauth(keys$key[1],
                    keys$key[2],
                    keys$key[3], 
                    keys$key[4])

```

Then write a regular expression you want to search twitter for, and use this as an input for `hash_sentiment()`

```{r, echo = TRUE}
hash_sentiment(regex = "coriander|cilantro", num.tweets = 800,
               method = "afinn", sentiment = "positive", num.summary = 3,
               scrape = TRUE)


```


If you want to look at different parts of the same twitter scrape, set `scrape = FALSE`

```{r, echo = TRUE}
hash_sentiment(regex = "coriander|cilantro", num.tweets = 800,
               method = "afinn", sentiment = "negative", num.summary = 3,
               scrape = FALSE)


```

Please excuse the swearing!!
